\documentclass[fontsize=9pt]{tccv}
\usepackage[english]{babel}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,     
	urlcolor=cyan,
}
\begin{document}

\part{Imaculate Mosha}

\personal
    [http://imaculate.github.io]
    {Washington, USA}
    {(+1) 425 703 8325}
    {imaculatemosha@yahoo.com}

\section{Technical experience}

\begin{eventlist}
\item{03/02/2020 -- Present}
	{Microsoft HQ, Redmond}
	 {Software Development Engineer II}

Working on Microsoft Word Graphics and Engaging Experiences Group.
Working on Word's backend to improve User Experience


\item{06/03/2019 -- 02/28/2020}
	 {Microsoft HQ, Redmond}
	 {Software Development Engineer}
	 
Worked in the Tools for Software Engineers Team (\href{ https://www.microsoft.com/en-us/research/project/tools-for-software-engineers/}{Page}), specifically CloudTest.
Designing and implementing distributed systems.
Reviewing code and mentoring junior members.

\item{10/02/2017 -- 05/31/2019}
	 {Microsoft Development Centre, Vancouver}
	 {Software Development Engineer}
	 
Worked remotely in the Tools for Software Engineers Team (\href{ https://www.microsoft.com/en-us/research/project/tools-for-software-engineers/}{Page}), specifically CloudTest.
Designing and implementing distributed systems.
Reviewing code and mentoring junior members.


\item{01/23/2017 -- 01/21/2017}
	 {Amazon Development Centre, CapeTown}
	 {Intern Software Development Engineer}
	 
Worked on the troubleshooting page for failures when connecting to EC2 instances.
Implemented with Java, CSS and internal framework.


\item{02/11/2016 -- 05/31/2016}
	 {Department of Computer Science, University of CapeTown}
	 {Research Assistant}
	 
Worked on a Simple Sequencing prototype, specifically Directed IMS sequencing for educators under the supervision of Dr.Hussein Suleiman.  
Implemented the web application using front-end web technologies and Nodejs framework. 


\item{11/30/2015 -- 02/12/2016}
     {j5 International \url{www.j5int.com}}
     {Software Development Intern}

Worked on enhacing the j5 Intergrated Development Environment(IDE) and bug fixes using wxpython.

\item{06/17/2015 -- 07/09/2015}
     {Digiata \url{www.digiata.com}}
     {Programmer Intern}

Implemented a framework for Object Relational Mapping using C\#.
Compared the performance Entity Framework Dapper, SqlFu, PetaPoco, Nhibernate and LightSpeed for the company tasks.

\item{12/09/ 2013 -- 01/17/2014}
     {Niafikra \url{www.niafikra.com}}
     {Intern developer}

Developed a web application, Autodeployer for deploying projects from Git/Bitbucket to the respective
production server. Available at \url{https://github.com/imaculate/Autodeployer}.

\item{02/09/2014 -- 05/29/2015}
     {University of CapeTown}
     {Course Tutor}

During semester time I tutored Computer Science and Electrical Engineering over the whole period. I ran tutorial sessions, supervised and marked labs and tests.

\end{eventlist}

\section{Leadership experience}

\begin{eventlist}
\item{December 2015 - 2016}
	{Women In Computer Science, UCT}
	{ChairPerson}
	
Fundraising and cordinating events with the committee

\item{September 2014 - July 2015}
{Google}
{Google Student Ambassador}

Founded the Google Students Club at UCT. Cordinated technical development events with support from Google.

\item{2014 - 2015}
{Student Orientation and Advocacy Centre, UCT}
{Orientation leader}

In February of the two years, I guided new students around University, in a team of selected students.

\end{eventlist}

\section{Education}

\begin{yearlist}

\item{2013 -- 2016}
     {BSc Electrical and Computer Engineering}
     {University of CapeTown, South Africa}

\item{2006 - 2012}
     {A-level Certificate}
     {Marian Girls' High School, Tanzania}

\end{yearlist}

\section{Technical Projects}

\begin{yearlist}

\item{2016}
     {Doublecheck(\href{http://devpost.com/software/doublecheck}{Link to devpost page})}
     {Outlook addin developed in online hackathon}

\item{2016}
     {Scikit-Learn (\href{https://github.com/imaculate/scikit-learn}{github.com/scikit-learn})}
     {Contributor to open source Machine Learning library}

\item{2015}
     {Accela(\href{https://github.com/JustOmondi/ES-project}{github.com/JustOmondi/ES-project})}
     {Audio Project for Embedded Systems course}

\item{2014}
{Footsteps (\href{http://devpost.com/software/footsteps}{devpost.com/software/footsteps})}
{Android app for happiness developed in online hackathon}

\item{2013}
     {Blogger (\href{http://technofunology.blogspot.co.za/}{technofunology.blogspot.co.za})}
     {A frequently updated blog showcasing my technical activities}

\end{yearlist}

\section{Awards and Distinctions}

\begin{factlist}
\item{2016}{Web Summit 2016 scholarship}
\item{2015}{Top 20 award for APL coding contest}
\item{2014, 2015}{Grace Hopper Conference Scholarship }
\item{2014}{Google Anita Borg scholarship}
\item{2013, 2014, 2015}{Class medalist for several courses, Dean's Merit List}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Proficient level}
     {Java, Python, C++ , Git, JavaScript}

\item{Intermediate}
     { C\#, VHDL , C, APL, Octave, Matlab,HTML, CSS, Groovy,
     Haskell, Scheme, GoogleApps Script,  Go, \LaTeX}

\end{factlist}


\section{References}
Available on request

\end{document}
